{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion}

### 2017-01-07 proposal/related.tex
more relwork on tm

\section{Other Techniques}

@@

Transactional memory (TM), first introduced in \cite{transactional-memory},
has received renewed attention in recent years with the announcement of Intel's Haswell architecture \cite{htm-haswell},
which promises to support hardware transactions using new {\tt x86} instructions.
%
The combination of TM and testing in the literature is sparse so far.
{\em Learning from Mistakes} \cite{learning-from-mistakes} is a study of the characteristics of many different types of concurrency bugs;
it found that TM could potentially fix some, but not all, of the studied bugs,
although in some cases it must be combined with other concurrency primitives,
which indicates a major need for verifying transactional code with model checking.

>>>>

\section{Other Concurrency Techniques}

@@

Transactional memory (TM), first introduced in \cite{transactional-memory},
has received renewed attention in recent years with the announcement of Intel's Haswell architecture \cite{htm-haswell},
which promises to support hardware transactions using new {\tt x86} instructions.
Because hardware transactions can fail for any reason, not just on memory conflicts,
software TM remains relevant,
and recent works such as \cite{hybrid-htm-stm} and \cite{stm-relaxed-memory} enhance it to be nested with hardware transactions, or to be used on weak memory architectures, respectively;
which in turn produce ever more complicated concurrency models for people like me to tackle.
%
Testing approaches to TM are sparsely represented in the literature so far.
%The Weakest Reasonable Condition
\cite{specifying-verifying-tm} introduces several conditions to help specify/verify the correctness of TM {\em implementations},
but not that of client programs which use TM.
{\em Learning from Mistakes} \cite{learning-from-mistakes} is a study of the characteristics of many different types of concurrency bugs;
it found that TM could potentially fix some, but not all, of the studied bugs,
although in some cases it must be combined with other concurrency primitives,
which indicates a major need for verifying transactional code with model checking.
